Reproducible Summary Tables with the gtsummary Package

### 2020-12-11 RJtemplate_gtsummary_submission.tex
overleaf

\begin{example}

\end{example}

ADD SOMETHING ABOUT as\_gt() and using the many fns available to us there.

>>>>

\begin{example}
trial %>%
  select(age, grade, trt) %>%
  tbl_summary(by = trt, missing = "no") %>%  
  add_overall() %>%    
  add_p() %>%      
  add_stat_label() %>%     
  modify_header(label ~ "**Variable**") %>%   
  modify_spanning_header(c(stat_1, stat_2) ~ "**Treatment Recieved**") %>%  
  as_gt() %>% 
  gt::tab_header(   
    title = gt::md("**Table 1. Patient Characteristics**"),
    subtitle = gt::md("_Highly Confidential_")
  ) %>%
  gt::tab_source_note("Data updated June 26, 2015")   
\end{example}
\begin{figure}[h!]
  \includegraphics[height=4cm]{custom.png}
  \centering
\end{figure}
